TBD

### 2021-02-26 outputs/paper/paper.Rmd
Reformatted graphs and written portion in Results section

Survey questions pertaining to the characteristics of the restaurants, such as location, size, type, and age of restaurants Figure \@ref(fig:samplechar) show us that:

* The largest concentration (nearly 60%) of restaurants in the Greater Toronto Area are centralized in downtown Toronto (28.26%), North York (15.78%), and Scarborough (13.74%); 
* Most restaurants are of medium or large scale^[The survey asked respondents to consider their restaurant scale in terms of space and seating capacity, however the perceptions of scale may be subjective]; 
* The majority of restaurants who responded are relatively new (Have been operating for 3 years or less); 
* Fast-food/quick service restaurants were the most common types, followed by casual dining, and then fine dining;
* UberEats was the most popular food courier service that restaurants received orders from. (MOVE)

@@

```{r Q4, echo = FALSE, message = FALSE, fig.cap = "Number of years restaurants have been in operation"}
### How many years has your restaurant been in operation?
### 1-4 years
### 5-7 years
### 8-10 years
### 10 or more years
q4 <- ggplot(data = all_simulated_dataset, mapping = aes (x = Q4, fill = type)) +
  geom_bar() + coord_flip() +
  scale_x_discrete(limit = c ("3 years or less", "5-7 years", "8-10 years", "10 or more years")) +
  labs(x = "Years of Operation",
       y = "# of Restaurants",
       fill = "Condition",
       title = str_wrap("Number of Years in Operation", 30)) +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) + 
  theme(title=element_text(size=9))
```
```{r samplechar, fig.width=9, fig.height=7, echo = FALSE, message = FALSE, fig.cap="Sample Characteristics of Restaurants by Condition"}
#combining plots for q1-4
grid.arrange(q1, q2, q3, q4)
```

@@

In terms of effects on revenue and/or overall sales for restaurants during the intervention period, Figure \@ref(fig:reveffects) shows us that more restaurants within the treatment group saw decreases in revenue compared to the prior quarter (July 1 - Sep 30), while the control group's revenue largely remained the same. In addition to this, it shows that of those restaurants that saw a decrease in revenue, the treatment group saw the harshest declines in revenue during the intervention period. A Chi-Square test for whether the restaurant saw a decrease in revenue showed that restaurants in the treatment group were more likely to report a decrease in revenue *X*^2^ (2, *N* = 330) = 220.73, *p* < 2.2e-16. The percentage decrease in revenues also showed a significant relationship, where restaurants in the treatment group are most likely to report higher loss of revenue during the intervention period *X*^2^ (3, *N* = 330) = 178.33, *p* < 2.2e-16. Prior to the intervention period, it appears as though both groups had similar breakdowns of revenue coming from take-out and/or delivery.

```{r Q7, echo = FALSE, message = FALSE}
### Between Oct 1 and Dec 31 was your total sales revenue higher, lower, or about the same as it was during the previous quarter (last quarter dates)? *
### Higher
### Lower
### Around the Same
q7 <- ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar() +
  labs(x = "Revenue Change",
       y = "# of Restaurants",
       title = "Revenue changes between Oct 1 and Dec 31",
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

@@

```{r Q8, echo = FALSE, message = FALSE}
### What was the approximate percentage decrease in total sales revenue between Oct 1 and Dec 31 compared to the during the previous quarter (last quarter dates)? *
### Decline of 50% or more
### Decline of 25% to 50%
### Decline of 10% to 25%
### Decline of 10% or less
q8 <- ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. % Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = str_wrap("Percentage of total sales revenue decrease between Oct 1 and Dec 31", 40),
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

@@

```{r Q9, echo = FALSE, message = FALSE}
### Before Oct 1st, approximately how much of your total monthly sales revenue came from takeout or delivery? *
### Did not offer takeout or delivery
### 25% or less
### 25- 50%
### 50-75%
### 75% or more

q9 <- ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = "stack") +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "25% or less", "25-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = str_wrap("Total revenue from takeout or delivery prior to Oct 1", 30),
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

```{r Q10, echo = FALSE, message = FALSE, fig.cap = "The most used food courier service"}
### Between Oct 1 and Dec 31, which food courier service did you receive the most orders from?
### UberEats
### SkiptheDishes 
### DoorDash
### Other
### In-house delivery service
### None
q10 <- ggplot(data = all_simulated_dataset, mapping = aes(x = Q11, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("UberEats", "SkiptheDishes", "DoorDash", "In-house delivery service", "Other", "None")) +
  labs(x = "Delivery Service",
       y = "# of Restaurants",
       title = "Food courier service popularity",
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) + 
  theme_fivethirtyeight()
```

```{r reveffects, fig.width=12, fig.height=8, echo = FALSE, message = FALSE, fig.cap="Effects on revenue as a result of intervention by condition"}
grid.arrange(q7, q8, q9, q10)
```

@@

* Most of the restaurants in the control group did not make any alterations to their menu prices, while most restaurants in the intervention group either lowered or raised the menu price;
* Most of the restaurants in the control group did not adjust their hours our days of operation, while most of the ones in the intervention group reduced their operating schedules.

```{r Q11, fig.height = 2.5, fig.width = 6, echo = FALSE, message = FALSE, fig.cap = "Menu adjustments during the intervention period (Oct 1 - Dec 31)"}
### Between (start date of intervention) and (end date of intervention), did you make any adjustments to your menu prices?
### Yes, prices were raised
### Yes, prices were lowered
### No changes were made
ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = str_wrap("Menu adjustments between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

@@

```{r opshourseffects, fig.width = 5, fig.height = 4.8, echo = FALSE, message = FALSE, fig.cap="Effects on hours and days of operation as a result of intervention by condition"}
grid.arrange(q12, q13)
```

@@

```{r opsdayseffects, fig.width = 6, fig.height = 4.8, echo = FALSE, message = FALSE, fig.cap="Effects on hours and days of operation as a result of intervention by condition"}
grid.arrange(q14, q15)
```

Pearson’s Chi-squared (*X*^2^) test was used to see if there is a statistically significant difference between the intervention and the adjustments of the restaurants. The test results show that the p-value of each of those adjustments is less than 0.001, meaning that there is a high correlation between those variables. Consequently, it is expected that restaurants will most likely adjust the menu price and reduce their operating schedule if they operate on a delivery and take-out only basis.

```{r Q16, echo = FALSE, message = FALSE}
### Have you applied for and received any external funding or grants for your restaurant since (intervention start date)?
### Yes
### No
ggplot(data = all_simulated_dataset, mapping = aes(x = Q16, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Application status",
       y = "# of restaurants",
       title = str_wrap("Funding Applications between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

>>>>

Survey questions pertaining to the characteristics of the restaurants, such as location, size, type, and age of restaurants Figure \@ref(fig:samplechar) and \@ref(fig:Q5)show us that:

* The largest concentration (nearly 60%) of restaurants in the Greater Toronto Area are centralized in downtown Toronto (28.26%), North York (15.78%), and Scarborough (13.74%); 
* Most restaurants are of medium or large scale^[The survey asked respondents to consider their restaurant scale in terms of space and seating capacity, however the perceptions of scale may be subjective]; 
* The majority of restaurants who responded are relatively new (Have been operating for 3 years or less); 
* Fast-food/quick service restaurants were the most common types, followed by casual dining, and then fine dining;
* During the intervention period, restaurants received the most orders via UberEats, followed by DoorDash, and then other food courier services;
* A small portion of restaurants utilized their own in-house delivery services, most of which were in the control group
* The distribution of these characteristics were roughly equal among restauraunts in both groups, meaning their sample characteristics are similar

@@

```{r Q4, echo = FALSE, message = FALSE, fig.cap = "Number of years restaurants have been in operation"}
### How many years has your restaurant been in operation?
### 1-4 years
### 5-7 years
### 8-10 years
### 10 or more years
q4 <- ggplot(data = all_simulated_dataset, mapping = aes (x = Q4, fill = type)) +
  geom_bar() + coord_flip() +
  scale_x_discrete(limit = c ("3 years or less", "5-7 years", "8-10 years", "10 or more years")) +
  labs(x = "Years of Operation",
       y = "# of Restaurants",
       fill = "Condition",
       title = str_wrap("Number of Years in Operation", 30)) +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) + 
  theme(title=element_text(size=9))
```

```{r samplechar, fig.width=9, fig.height=7, echo = FALSE, message = FALSE, fig.cap="Sample Characteristics of Restaurants by Condition"}
#combining plots for q1-4
grid.arrange(q1, q2, q3, q4)
```

```{r Q10, echo = FALSE, message = FALSE, fig.cap = "The most used food courier service", fig.width=5, fig.height=3.5}
### Between Oct 1 and Dec 31, which food courier service did you receive the most orders from?
### UberEats
### SkiptheDishes 
### DoorDash
### Other
### In-house delivery service
### None
ggplot(data = all_simulated_dataset, mapping = aes(x = Q11, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("UberEats", "SkiptheDishes", "DoorDash", "In-house delivery service", "Other", "None")) +
  labs(x = "Delivery Service",
       y = "# of Restaurants",
       title = "Food courier service popularity",
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) + 
  theme_fivethirtyeight() +
  theme(title=element_text(size=9))
```

@@

In terms of effects on revenue and/or overall sales for restaurants during the intervention period, Figure \@ref(fig:reveffects) shows us that more restaurants within the treatment group saw decreases in revenue compared to the prior quarterly revenue in which they were offering their full services (July 1 - Sep 30), while the control group's revenue largely remained the same compared to their previous quarterly revenue. In addition to this, for restaurants that saw a decrease in revenue, the intervention group saw the harshest declines (declines of around 50%) in revenue during the intervention period. A Chi-Square test for whether the restaurant saw a decrease in revenue showed that restaurants in the treatment group were more likely to report a decrease in revenue *X*^2^ (2, *N* = 330) = 220.73, *p* < 2.2e-16. The percentage decrease in revenues also showed a significant relationship, where restaurants in the treatment group are most likely to report higher loss of revenue during the intervention period *X*^2^ (3, *N* = 330) = 178.33, *p* < 2.2e-16. Prior to the intervention period, it appears as though both groups had similar breakdowns of revenue which came from take-out and/or delivery as shown in Figure \@ref(fig:Q9).

```{r Q7, echo = FALSE, message = FALSE}
### Between Oct 1 and Dec 31 was your total sales revenue higher, lower, or about the same as it was during the previous quarter (last quarter dates)? *
### Higher
### Lower
### Around the Same
q7 <- ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar() +
  labs(x = "Revenue Change",
       y = "# of Restaurants",
       title = "Revenue changes between Oct 1 and Dec 31",
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme(title=element_text(size=9))

@@

```{r Q8, echo = FALSE, message = FALSE}
### What was the approximate percentage decrease in total sales revenue between Oct 1 and Dec 31 compared to the during the previous quarter (last quarter dates)? *
### Decline of 50% or more
### Decline of 25% to 50%
### Decline of 10% to 25%
### Decline of 10% or less
q8 <- ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. % Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = str_wrap("Percentage of total sales revenue decrease between Oct 1 and Dec 31", 40),
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme(title=element_text(size=9))

@@

```{r reveffects, echo = FALSE, message = FALSE, fig.height=5, fig.width=5, fig.cap="Changes in Revenue During Intervention Period"}
grid.arrange(q7, q8)
```

```{r Q9, echo = FALSE, message = FALSE, fig.cap="Take-out and Delivery Sales Before the Intervention", fig.width=5, fig.height=3}
### Before Oct 1st, approximately how much of your total monthly sales revenue came from takeout or delivery? 
### Did not offer takeout or delivery
### 25% or less
### 25- 50%
### 50-75%
### 75% or more

ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = "stack") + coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "25% or less", "25-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = str_wrap("% of Revenue from Take-Out/Delivery Before Intervention", 30), 
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme(title=element_text(size=9))
```

@@

* Most of the restaurants in the control group did not make any alterations to their menu prices, while most restaurants in the intervention group made alterations by raising or lowering prices, more of which chose to reduce their menu prices
* Most of the restaurants in the control group did not adjust their hours or days of operation, while most of the ones in the intervention group reduced their operating schedules
* For restaurants who reduced their hours of operation, most restaurants reduced their hours by 15%-30%, followed by 30%-50%
* Most restaurants who reduced their days of operation did so by 1-2 days

Pearson’s Chi-squared (*X*^2^) tests were conducted to see if there is a statistically significant difference between responses regarding restaurant adjustments in the intervention and control conditions. The test results show that the p-value of each of those adjustments is less than 0.001, meaning there is a significant relationship between condition (whether not not indoor dining services were shut down or not) and adjustments made to menu prices, hours of operation, and days of operations. That is, restaurants in the intervention condition were more likely to change their menu prices and reduce their operational hours and days.

These results suggest restaurants in the intervention condition who had to shutdown their indoor dining services had to make several changes to their business practices to account for the circumstances of the intervention and the loss of revenue which previously came from indoor dining. For instance, menu prices might have been lowered to entice more customers, and opening hours and days may have been reduced to help save on operational costs. However, this information does not tell us when exactly these adjustments were made, only that they occurred at some point in the intervention period. This means we cannot tell if restaurants made these changes early on in the study as a precautionary measure, or if the changes were made later in the study period as a reactionary measure to make up for losses the restaurants had been experiencing as a result of the intervention.

```{r Q11, fig.height = 3.5, fig.width = 5, echo = FALSE, message = FALSE, fig.cap = "Menu adjustments during the intervention period (Oct 1 - Dec 31)"}
### Between (start date of intervention) and (end date of intervention), did you make any adjustments to your menu prices?
### Yes, prices were raised
### Yes, prices were lowered
### No changes were made
ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = str_wrap("Menu adjustments between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight() +
  theme(title=element_text(size=9))

@@

@@

```{r opshourseffects, fig.height=3.5, fig.width=8, echo = FALSE, message = FALSE, fig.cap="Effects on hours and days of operation as a result of intervention by condition"}
grid.arrange(q12, q13, ncol = 2)
```

```{r opsdayseffects, fig.height=3.5, fig.width=8, echo = FALSE, message = FALSE, fig.cap="Effects on hours and days of operation as a result of intervention by condition"}
grid.arrange(q14, q15, ncol = 2)
```

Finally, we encouraged restaurants who partook in the intervention to seek out external funding and grant opportunities during the intervention if they were concerned about their restaurants' financial obligations during the study. Figure \@ref(fig:opsdayseffects) indicates most restaurants in the intervention condition did apply for and receive external grants and funding during the study compared to restaurants in the control group. Again, this doesn't indicate when exactly they applied for and received the money, only that it occurred sometime in the three month period. This means many restaurants could have applied for the grants early on in the study period as they were anticipating their financial losses, or some had to apply for opportunities at a later period in the study after already experiencing consistent losses.

```{r Q16, echo = FALSE, message = FALSE, fig.width=5, fig.height=3.5, fig.cap="Proportion of Restaurants who Applied and Received Funding During Study"}
### Have you applied for and received any external funding or grants for your restaurant since (intervention start date)?
### Yes
### No
ggplot(data = all_simulated_dataset, mapping = aes(x = Q16, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Application status",
       y = "# of restaurants",
       title = str_wrap("Restaurants who Received External Funding During Study", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```
